% Conclusion
% • Conclusion of the project objectives
% • Any other possible future enhancements

\chapter{Conclusion}\label{ch:Conclusion}

\section{Summary of our Application}\label{summary_app}
% added a draft here, can yall read and see how isit - Jovian
For individuals seeking an application that revolutionizes their study methods towards greater efficiency and efficacy, "Study Together" presents itself as the quintessential solution. This application is meticulously crafted to facilitate a seamless transition for students entering the realm of higher education, to cultivate a dynamic online platform for the exchange of knowledge, and to deliver prompt resolutions to academic inquiries.

The application is equipped with a comprehensive array of sophisticated functionalities, including Firebase and Firestore for robust authentication processes, integration of Gemini AI, and Wolfram Alpha to furnish AI-driven responses and specialized support for mathematical queries. Enhanced by Optical Character Recognition (OCR) technology, "Study Together" allows for the swift capture, cropping, and uploading of images pertaining to complex questions, significantly simplifying the process of obtaining assistance for detailed and elaborate academic problems.

Additionally, the application offers an in-built chat feature that promotes real-time dialogue among users, fostering a space for the discussion of scholarly obstacles or for the mere purpose of engaging with fellow members of the educational community. This is supplemented by a daily notification system that provides users with timely updates on new content from their followed contacts, thereby keeping them informed of ongoing dialogues and educational content.

In summary, "Study Together" extends beyond the functionality of a mere application; it serves as a steadfast academic ally, endowing users with an array of instrumental tools and a supportive community network to accompany them throughout their educational pursuits.


\section{Future Enhancements}\label{future_enhancements}

% drafted future enhancements here tgt with rq's ocr - Jovian
In future developments, we plan to enhance the notification system by adding interactive features that enable users to mark notifications as read or bookmark them for later perusal directly within the notification interface. Such advancements are in line with our ongoing commitment to refine the app based on user feedback and preferences, prioritizing ease of use and continuous engagement to ensure that updates effectively address the needs of our community. This process of iterative improvement underscores our dedication to delivering a user experience on the "Study Together" platform that is both seamless and compelling.

Regarding the OCR functionality, we recognize that the processing time is significantly affected by the image size. Although we have implemented a cropping function to mitigate this, processing large blocks of text remains challenging. Future considerations will include additional pre-processing steps like image scaling or compression to enhance processing speed. The current system's limitations in recognizing handwritten text, due to the constraints of the TessBase API, are also acknowledged. To overcome these challenges, we are considering the exploration of alternative OCR libraries or frameworks that may offer improved accuracy. For particularly complex or specialized text recognition tasks, developing a custom OCR model presents itself as a promising solution, offering the potential to significantly enhance the platform's capability to accurately process a wider range of textual inputs.

Another potential enhancement with regards to elevating the display of math formulas and associated content within math question answers is to integrate with a technology like MathView, a library designed for Android applications, which supports LaTeX syntax for formulas. By integrating MathView, users would enjoy a more seamless and visually appealing experience when viewing and interacting with math content. Moreover, incorporating features such as the ability to zoom in or out on formulas, highlight specific parts of a formula, or animate the steps of solving a math problem could further enrich the user experience, making the app more engaging for students studying math related questions.


%future work for OCR if needed%
% The processing time of the OCR is greatly influenced by the size of the image. Although a cropper function is implemented to potentially address such issue, recognising huge block of text is still a challenging task. Additional pre-processings such as image scaling or compressing can be considered to improve the processing time. The function also lacks on the ability to accurately recognise hand-written text, constrained by the capability of the TessBase API. To mitigate the limitations encountered in text recognition, especially with hand-written text, exploring alternative OCR libraries or frameworks could be beneficial. Additionally, for highly specialized or challenging tasks, training a custom OCR model could be a viable option.
