% System Architecture & Implementation
% • System architecture diagram
% • Description of the architecture and implementation details
% • Description on how the app employs four or more of the advanced mobile
% features (networking, sqlite database, gps, etc.)
% • Third party libraries, code or tools used in the application
% • Any special algorithms or methods used
% • (All other full diagrams to be placed in the appendix

\chapter{Implementation}\label{implementation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% System Architecture
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\import{Sections/}{Software_Architecture}

\section{Technology Stack}

The technology stack employed in this solution is carefully curated to enhance the application's functionality while adhering to the specified design requirements and themes.

At the core of this stack lies \textbf{Firebase}, serving as a robust foundation for networking functionalities. Leveraging \textbf{Firestore} ensures seamless data exchange and real-time updates, complemented by the secure access control provided by Firebase's authentication module. Moreover, \textbf{Firebase Storage} facilitates efficient storage of multimedia content, enhancing user experience with seamless access to resources.

For local data management and caching, the application integrates \textbf{Room DB Cache}, tailored specifically for handling user-related data. By utilizing Room, the app ensures efficient storage and retrieval of user information, thereby optimizing performance and responsiveness.

To support academic pursuits, the integration of \textbf{OCR} technology is pivotal. This feature enables the conversion of printed or handwritten text into digital formats and incorporates multimedia functionalities. Leveraging networking capabilities, the OCR module downloads online resources (model) while employing \textbf{coroutinescope} for optimized multithreading performance. Additionally, real-time text recognition is facilitated through camera integration, enhancing user accessibility to study materials.

In enhancing the educational experience, the application seamlessly integrates with Retrofit for API calls to educational services like Wolfram|Alpha, particularly for math-related queries. This integration enables the retrieval of relevant educational content, enriching the depth and breadth of the user's learning journey.

Lastly, the inclusion of \textbf{Gemini AI SDK library} elevates the application's capabilities by incorporating advanced AI functionalities. This integration empowers the application to offer personalized recommendations, intelligent insights, and adaptive learning experiences, aligning with the overarching goal of delivering a comprehensive educational platform.

Each functionality implemented was carefully considered for its seamless integration into the user's workflow within the application. While the application mirrors the look and feel of popular social media platforms like Instagram for personalization, additional functionalities such as Text-to-Speech were omitted in favor of Google's GBoard, which provides efficient implementation. Furthermore, OCR Technologies are implemented with privacy in mind, ensuring local processing and the removal of images after processing.


\section{Firebase Services}

Firebase serves as the backbone of our application, providing a secure and scalable infrastructure that caters to our authentication, database, and media storage needs.

\subsection{Firebase Authentication}

Our authentication system is powered by Firebase and RoomDB, combining their strengths to ensure a seamless and secure user experience. Firebase Authentication offers robust email/password sign-in methods, providing users with a straightforward way to access the platform.

Upon successful authentication, Firebase manages user states and details, while RoomDB serves as a local cache, storing user credentials for automatic login on subsequent app launches. This enhances user convenience by eliminating the need for repeated authentication.

During app initialization, if RoomDB contains user information, users are automatically logged in, with additional user details retrieved from Firestore for centralized management and accessibility across the application.

This integration streamlines authentication while enhancing security and reliability, with Firebase providing additional features such as hashing, password reset, and secure user details storage.

\subsection{Firebase Storage}

Firebase Storage is utilized for storing user profile pictures within the application. It provides a reliable and scalable solution for securely storing and accessing profile images, facilitating easy personalization of user profiles.

Upon profile creation or modification, profile pictures are uploaded to Firebase Storage, ensuring efficient management of multimedia content. This approach enhances user experience by enabling seamless profile customization.

Leveraging Firebase Storage offers robust storage capabilities, straightforward access controls, and seamless integration with other Firebase services, ensuring secure and readily accessible profile pictures.

\subsection{Firebase Firestore}

Firebase Firestore acts as the primary document database for storing various data within the application. It facilitates the storage of user-related information, including usernames, followers, following, chats, and metadata essential for user interactions.

Moreover, Firestore powers the Q\&A functionality by storing question titles, descriptions, tags, and answers, enabling users to post and access questions and answers seamlessly, fostering a collaborative learning environment.

Additionally, Firestore enables real-time communication through its integration with the chat feature, allowing users to engage in private conversations and community building within the platform.

By leveraging Firestore's scalability, real-time updates, and integration with other Firebase services, the application ensures efficient data storage and retrieval, contributing to a dynamic and engaging user experience.



% add main app above %
\section{Optical Character Recognition Module}
Our application is integrated with the Optical Character Recognition (OCR) technology. This capability allows users to easily convert text in images into editable text directly within the app. It is primarily demonstrated within the question posting section, for the users to post questions they found online or from the textbook. This enhancement draws inspiration from the Android-OCR project by Achmad Qomarudin.

For seamless image-to-text conversion, we've integrated TessBaseAPI into our system. Given the necessity for processing images locally, it's essential to have access to pre-trained data in the local environment. To achieve this, we provided an option to download the data file through a dedicated download manager, which operates within a CoroutineScope. This approach ensures that users has the freedom to choose not to download the additional resources, and if they are keen, they will be kept informed of the download progress via the UI. It's important to note that skipping the download will disable the OCR feature. The data will be verified each time the OCR activity initiates, and if the data is missing or corrupted, the download process will be automatically triggered again.

Given that images may contain unnecessary visual elements, we've incorporated a cropping tool. This tool, powered by the Android-Image-Cropper library, helps users isolate the text they wish to convert. This functionality is not limited to OCR; it's also implemented for profile picture uploads. User can zoom in and out, flip or rotate the image before it is processed.

To further boost the precision of our OCR, we've implemented basic image pre-processing. This includes adjusting the image's grayscale before conversion, to reduce the noise from the backgound. All temporary files are stored in local storage and will be automatically deleted once the activity finishes.

After the OCR function converts the image to text, the result text can be viewed and edited in a separate page, togather with the cropped image for reference. In this page, the image can be zoomed in and out, and move freely within the container, for user to reference to, in the event of them needing to edit the text recognised. If the user is satisfied with the result, upon clicking proceed button, the text will be automatically transferred to the caller activity within the application using the Intent putExtra method, and show in the respective text field. This ensures a smooth and efficient workflow, where users can easily view and verify the converted text, then quickly move from capturing or selecting an image to utilizing the extracted text in their posts or queries, enhancing the overall user experience.

User consent is crucial in mobile application, especially regarding the download of supplementary data as well as accessing the camera and gallery. All necessary permissions will be asked, including the right to download, open camera and access the photos, before carrying out the activities.

Dagger Hilt for dependency injection is implemented within the OCR module. Although the specifics of Dagger Hilt's application in this context might not be immediately apparent, it serves a critical role in simplifying dependency management. By using Dagger Hilt, we were able to streamline the process of providing dependencies for the OCR functionality, such as the TessBaseAPI and the download manager for training data. This not only makes the codebase modular and easier to maintain but also improves the scalability of our application.

\section{Gemini Artificial Intelligence Service}

The Gemini Artificial Intelligence (AI) service stands as a cornerstone in our application, enriching the user experience with advanced capabilities for knowledge exchange. Powered by sophisticated algorithms, the Gemini AI SDK delivers precise and insightful responses to a wide array of queries within 'Study Together', covering diverse subjects and topics. This service plays a pivotal role in enhancing the efficiency of knowledge exchange, especially in scenarios where users require immediate answers or face unanswered questions.

Integrated seamlessly into the question details screen, the Gemini AI service offers users a streamlined experience for accessing both the question and its answers. With a simple click, users can leverage the AI service to receive additional insights and information related to the current question. This integration not only enhances user experience but also provides quick and convenient access to valuable knowledge, thereby fostering a more enriched learning environment.

Moreover, the Gemini AI service brings unparalleled convenience to users by eliminating the need to search elsewhere, such as on Google or ChatGPT, for answers. This saves users time and spares them the trouble of navigating multiple sources. Additionally, the answers generated by the Gemini AI service are more accurate and reliable compared to answers provided by users, ensuring that users receive high-quality information tailored to their queries.

\section{Wolfram|Alpha Network Retrofit Service}

The Wolfram|Alpha Network Retrofit Service employs networking advanced mobile features to enhance the user experience. This service is seamlessly integrated into the application to augment the capabilities of the Gemini AI service, particularly for math-related queries. As a failover mechanism, it ensures that users always receive accurate answers to their math questions, even when the Gemini AI encounters limitations. 

Implemented using the Retrofit library, this integration allows for easy API calls to the Wolfram|Alpha short answers API over the network. When a math-related query causes the Gemini AI service to fail to respond correctly, the application automatically switches to the Wolfram|Alpha Retrofit Service to fetch the answer, thereby improving the user experience. By leveraging Wolfram|Alpha's expertise in mathematical computations, this integration enriches the user's learning experience by providing comprehensive support for a wide range of questions. This networking advanced mobile feature ensures reliable and efficient communication with external services, enhancing the overall functionality and usability of the application.

\section{Design, Flow, and Personalization}

Our application's design draws heavily from Human-Computer Interaction (HCI) concepts, with a particular focus on utilizing pastel colors renowned for their soothing and visually appealing properties. Inspired by the Catppuccin Theme, known for its pastel color palette, our design aims to establish a serene and inviting user interface. To achieve this, we utilized a sample image featuring Catppuccin-inspired colors to create a cohesive color scheme for our application using the Material Theme Builder, ensuring visual coherence and harmony throughout the interface.

The flow of our application mirrors that of popular social media platforms like Instagram and Reddit, featuring a familiar bottom navigation layout for seamless navigation. Utilizing key sections such as User Profiles, Home Page, and Explore, we leverage users' existing familiarity with similar functionalities, promoting easy recognition and intuitive usage—an essential aspect of HCI that enhances user engagement and retention. Concepts such as adding questions, following users, or editing profiles are integrated based on the existing knowledge our target audience possesses, providing a sense of familiarity rather than novelty.

In our design strategy, we incorporated elements such as Composable surfaces, cards, and boxes to create a structured and layered layout, facilitating usability by offering clear differentiation between various components and features. Inspired by leading social media platforms like Reddit and Instagram, our aim was to craft an aesthetically pleasing interface that encourages user interaction and participation, fostering an environment conducive to learning.

Overall, our design embodies a purposeful integration of HCI principles, pastel color palettes, and design elements inspired by established social media platforms. The result is an engaging and visually satisfying user experience tailored to support learning and collaboration.


\section{Foreground Notification Service}

% need to mod this still to talk more about the implementation (technical) aspect - Jovian
% Our application's notification service is developed with user autonomy and privacy at its core, only activating when a user grants permission within the app settings. This level of user control extends to their ability to opt out at any time, upholding our commitment to privacy and adherence to data protection regulations. Notifications are thus a reflection of our respect for the user's right to choose how and when to be informed about activity in the community.

% The daily updates feature is a curated digest of new questions posted by followed accounts, designed to provide information without overwhelming users with frequent alerts. By delivering these summaries once a day, we prevent an overabundance of notifications that could disrupt the user experience. The design of the notifications themselves is minimalist and informative, showing the poster’s profile picture, name, and the subject of the question, allowing users to quickly gauge the day's content at a glance.

% This approach to notifications serves to create a streamlined, interruption-free environment, offering users a simple yet effective means of staying up-to-date with community discussions, reflective of their interests and interactions, while preserving the sleek, user-friendly interface of our application.

Harnessing the capabilities of Android's ecosystem, our application's notification service is ingeniously integrated using the NotificationManager system. This allows users to tailor their notification experience directly within the system's settings, ensuring their control over the notifications' visibility and significance.

The service is enshrined within a Service class, allowing it to operate independently from the user interface. It performs in the background with discretion, routinely checking for new content while judiciously managing battery and data consumption through Android's JobScheduler. The delivery of daily notifications is precisely timed using a Handler and Looper mechanism, ensuring reliability. PendingIntent is employed to deliver a seamless transition for users from the notification back to the application.

The service skillfully assembles notifications, infusing them with the most recent and relevant user data to create a NotificationParcel. With the assistance of Glide, a formidable image processing library, profile pictures are swiftly loaded and cached, minimizing load times and data usage. This content is presented within a RemoteViews layout, which is crafted to allow users to swiftly understand and engage with the day's essential information.

The design of the notifications adheres to the Material Design guidelines, ensuring consistency in look and feel across different Android devices. Notifications feature a properly scaled app icon to reinforce brand identity, along with BigTextStyle to allow for an expanded view of the content when interacted with.

This technical execution, coupled with a staunch commitment to user privacy and autonomy, ensures that the service is initiated only after users have given explicit consent through the app settings, aligning with our stringent privacy policies and data protection standards. The daily summary feature thoughtfully compiles new contributions from monitored sources, maintaining a delicate equilibrium between user engagement and the avoidance of excessive notification alerts. The streamlined design of the notifications, which showcases only the essential elements like the author's profile image, name, and topic, signifies our commitment to a minimalist and informative user interface.

Overall, our notification service is more than a mechanism; it embodies our broader aspiration for an attentive and uninterrupted user journey. This service is a testament to our investment in user-oriented customization, sophisticated technical design, and a deep respect for users' desires for a non-disruptive yet enriching experience with the app.

