% Requirements & User Stories
% • Any requirements elicitation or how the features were selected
% • How the requirements were transformed to the user stories, description of the
% user stories and how they were selected
% • Each user story contains a title, description and acceptance criteria
% • (Excerpt of main user stories, full user stories to be placed in the appendix

\chapter{Requirements}\label{requirements}

\section{Requirements Elicitation and Selection}

% modified this part to add about the survey data in here %
With reference to the survey data responses outlined in Appendix \ref{appendix_a}, the project's specifications were shaped by an evaluation of the obstacles encountered by incoming students at SIT, as well as their requirements for academic assistance while adapting to university life. The primary focus was on addressing the following key areas:

\begin{itemize}
  \item Efficient assistance for understanding challenging study concepts.
  \item Access to comprehensive learning resources tailored to diverse learning styles.
  \item Facilitation of peer support and collaboration among students.
  \item Seamless connection and collaboration with peers on academic topics.
  \item Integration of a dedicated time management tool to balance academic and personal responsibilities.
\end{itemize}

These requirements were translated into user stories to provide a clear understanding of the desired features and functionalities of the application.

\section{User Stories}

\subsection{User Story 1: Assistance in Learning}

\textbf{Title:} Efficient Assistance for Challenging Concepts \\
\textbf{Description:} As Alex, I seek a platform to efficiently connect with peers or tutors for assistance in understanding challenging study concepts. The ability to post specific questions, receive timely responses, and engage in meaningful discussions is crucial for overcoming academic hurdles. \\
\textbf{Acceptance Criteria:} 
- Users can post specific questions on the platform.
- Users receive timely responses from peers or tutors.
- Discussions on the platform are meaningful and contribute to understanding challenging concepts.

\subsection{User Story 2: Effective Learning Resources}

\textbf{Title:} Comprehensive Learning Resources \\
\textbf{Description:} In the pursuit of effective learning, I, as Alex, look for a platform with accessible and comprehensive learning resources. A system recognizing diverse learning styles and offering personalized educational tools ensures a more efficient and rewarding academic experience. \\
\textbf{Acceptance Criteria:} 
- The platform provides access to a variety of learning resources.
- Learning resources are tailored to diverse learning styles.
- Users can access personalized educational tools based on their preferences.

\subsection{User Story 3: Peer Support Platform}

\textbf{Title:} Collaborative Peer Support \\
\textbf{Description:} As a student like Alex, I value a peer support platform for academic discussions. A space for engaging in meaningful conversations, sharing insights, and collectively tackling challenging topics fosters a sense of community, providing valuable academic assistance and building connections. \\
\textbf{Acceptance Criteria:} 
- The platform facilitates meaningful conversations among peers.
- Users can share insights and collectively tackle challenging topics.
- The platform fosters a sense of community and builds connections among users.

\subsection{User Story 4: Seamless Collaboration}

\textbf{Title:} Effortless Topic Following \\
\textbf{Description:} Recognizing the significance of collaboration in successful learning, I, as Alex, envision a platform that effortlessly connects me with peers. A streamlined system allowing me to follow topics created by other users, engage in discussions, and collaboratively explore diverse subjects ensures a collective learning journey and establishes connections with fellow students. \\
\textbf{Acceptance Criteria:} 
- Users can follow topics created by other users.
- The platform facilitates discussions and collaboration on diverse subjects.
- Users can engage in a collective learning journey and establish connections with fellow students.

\subsection{User Story 5: Time Management Tool}

\textbf{Title:} Effective Time Management \\
\textbf{Description:} Recognizing the challenges of managing time effectively, I, as Alex, require a dedicated time management tool. This tool, featuring task tracking, study logs, and personalized study plans, significantly contributes to balancing academic responsibilities, extracurricular activities, and personal time. \\
\textbf{Acceptance Criteria:} 
- The platform includes a dedicated time management tool.
- Users can track tasks and activities.
- Personalized study plans are available to help users balance academic responsibilities and personal commitments.
